---
title: "Initial analysis"
author: César Soto Valero
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    css: main.css
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: false
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Import the header 
source("header.R")
# Clear the R environment
rm(list=ls())
```

# Prepare dataset 

The raw dataset has 613 libs GAV with information of the following variables:

```{r echo=FALSE}
# Read the data
raw_results <- read.delim("Data/raw_results.csv", sep = ",", header = T)

# Prepare the data
raw_results <- raw_results %>%
  mutate(Lib = paste(Lib_groupId, Lib_artifactId, sep = ":")) %>% 
  mutate(Lib_gav = paste(Lib, Lib_version, sep = ":")) %>% 
  mutate(Client = paste(Client_groupId, Client_artifactId, sep = ":"))

raw_results$Lib_groupId <- NULL
raw_results$Lib_artifactId <- NULL
raw_results$Lib_version <- NULL
raw_results$Client_groupId <- NULL
raw_results$Client_artifactId <- NULL

# View(raw_results)
# raw_results %>% count(Lib_gav)

colnames(raw_results)
```

We exclude the libs with `Size_debloat_jar == 0` and `Nb_classes_original == 0`, this results in a dataset with 72 diferent libs and 468 libs GAV

```{r echo=FALSE}
results <- raw_results %>%
  filter(Size_debloat_jar > 0 & Nb_classes_original > 0) %>%
  select(
    "Lib_gav"      ,
    "Lib"  ,
    "Client" ,
    "Size_original_jar",
    "Size_debloat_jar",
    "Nb_classes_original" ,
    "Nb_methods_original"   ,
    "Nb_classes_debloated"  ,
    "Nb_methods_debloated" ,
    "Lib_coverage"   ,
    "Client_original_test_error"  ,
    "Client_original_test_failing",
    "Client_original_test_passing",
    "Client_debloat_test_error"  ,
    "Client_debloat_test_failing" ,
    "Client_debloat_test_passing" ,
    "Client_coverage"      ,
    "Cover_lib"
  )           

# results %>% count(Lib_gav)

# View(results)

results
```

# Distribution of clients per library

The lib `commons-io:commons-io:2.4` has the larger number of clients with 874, followed by `commons-cli:commons-cli:1.2` with 279, and `commons-codec:commons-codec:1.10` with 257.

```{r echo=FALSE}
results %>% 
  count(Lib_gav) %>% 
  ggplot(aes(x= "Libs", y = n)) +
  geom_violin(fill="goldenrod") +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  xlab(NULL) +
  ylab("#Clients")+
  coord_flip()

results %>% 
  count(Lib_gav) %>% 
  arrange(desc(n))
```


# Library plots

## Size of the original vs size debloated

The size of the debloated jar is slightly bigger than the original one. It seems that JDBL is adding some dependencies or resourses that should't be included in the bundled jar. We need to invesitigate this in more details.

```{r echo=FALSE}
results_size <- results %>% select(Lib_gav, Size_original_jar, Size_debloat_jar) %>% 
  gather(libs, size, Size_original_jar:Size_debloat_jar) %>% 
  distinct() 

# violin plot of the sizes
violinplot_size <- results_size %>%  ggplot(aes(x = libs, y =size, fill = libs)) +
   geom_violin() +
  geom_boxplot(width = 0.1) +
   scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  coord_flip() +
  ylab("Libs") +
  xlab(NULL) +
  theme(legend.position = "none")

violinplot_size

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_size.pdf", plot = violinplot_size ,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

Let's see wich are those libraries for which the debloated jar is bigger than the original one.

```{r echo=FALSE}

results_size <- results %>% 
  filter(Size_original_jar < Size_debloat_jar) %>% 
  mutate (Diff_size = Size_debloat_jar - Size_original_jar) %>% 
  select(Lib_gav, Size_original_jar, Size_debloat_jar, Diff_size) %>% 
  distinct() %>% 
  arrange(desc(Diff_size))

results_size
```

Let's see plot the difference in size between the debloatead and the original JARs.

```{r echo=FALSE}
results_size <- results %>% 
  # filter(Size_original_jar < Size_debloat_jar) %>% 
  mutate (Diff_size = Size_debloat_jar - Size_original_jar) %>% 
  mutate (SizeType = ifelse(Diff_size > 0, "above", "below")) %>% 
  select(Lib_gav, Diff_size, SizeType) %>% 
  distinct()

barplot_size <- ggplot(results_size, aes(x=Lib_gav, y=Diff_size, label=Diff_size)) + 
  geom_bar(stat='identity', aes(fill=SizeType), width=.5)  +
  scale_fill_manual(name="Size", 
                    labels = c("Above Original", "Below Original"), 
                    values = c("above"="#00ba38", "below"="#f8766d")) + 
  coord_flip() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

barplot_size

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_size.pdf", plot = barplot_size , 
       height = 10, width = 7,  units = c("in"), device=cairo_pdf)
```

## Number of classes in the original vs number classes debloated

```{r echo=FALSE}
results_classes <- results %>% 
  select(Lib_gav, Nb_classes_original, Nb_classes_debloated) %>% 
  gather(libs, classes, Nb_classes_original:Nb_classes_debloated) %>% 
  distinct()

# violin plot of the classes
violinplot_classes <- results_classes %>%  ggplot(aes(x = libs, y = classes, fill = libs)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values = c("goldenrod","dodgerblue3")) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  coord_flip() +
  theme(legend.position = "none")

violinplot_classes

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_classes.pdf", plot = violinplot_classes,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```


```{r echo=FALSE}

# barplot of the classes
barplot_classes <- results_classes %>%  
  ggplot(aes(x = reorder(Lib_gav, classes), y = classes, fill = libs)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "libs") +
  coord_flip() +
  scale_fill_manual(values = c("goldenrod","dodgerblue3")) +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6))

barplot_classes

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_classes.pdf", plot = barplot_classes , 
       height = 10, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
perc_reduction_classes <- results %>% 
  select(Lib_gav, Nb_classes_original, Nb_classes_debloated) %>% 
  mutate(Perc_reduction = ((Nb_classes_original - Nb_classes_debloated)/Nb_classes_original)*100) %>% 
  select(Lib_gav, Perc_reduction) %>% 
  distinct()

# barplot of the methods
barplot_perc_reduction_classes <- perc_reduction_classes %>% 
  ggplot(aes(x = reorder(Lib_gav, Perc_reduction), y = Perc_reduction)) +
  geom_bar(stat = "identity", position = position_dodge(), fill = "dodgerblue3") +
  labs(x = "libs") +
  coord_flip() +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6)) +
  ylab("%Reduction of #Classes") 

barplot_perc_reduction_classes
```


## Number of methods in the original vs number of methods in the debloated

```{r echo=FALSE}
results_methods <- results %>% 
  select(Lib_gav, Nb_methods_original, Nb_methods_debloated) %>% 
  gather(libs, methods, Nb_methods_original:Nb_methods_debloated) %>% 
  distinct()

# violin plot of the methods
violinplot_methods <- results_methods %>% 
  ggplot(aes(x = libs, y = methods, fill = libs)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  coord_flip() +
  theme(legend.position = "none")

violinplot_methods

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_methods.pdf", plot = violinplot_methods,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
# barplot of the methods
barplot_methods <- results_methods %>%  ggplot(aes(x = reorder(Lib_gav, methods), y = methods, fill = libs)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "libs") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6))

barplot_methods

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_methods.pdf", plot = barplot_methods, 
       height = 10, width = 7,  units = c("in"), device=cairo_pdf)
```
Percentage of methods reduced per library.


```{r echo=FALSE}
perc_reduction_methods <- results %>% 
  select(Lib_gav, Nb_methods_original, Nb_methods_debloated) %>% 
  mutate(Perc_reduction = ((Nb_methods_original - Nb_methods_debloated)/Nb_methods_original)*100) %>% 
  select(Lib_gav, Perc_reduction) %>% 
  distinct()

# barplot of the methods
barplot_perc_reduction_methods <- perc_reduction_methods %>% 
  ggplot(aes(x = reorder(Lib_gav, Perc_reduction), y = Perc_reduction)) +
  geom_bar(stat = "identity", position = position_dodge(), fill = "dodgerblue3") +
  labs(x = "libs") +
  coord_flip() +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6)) +
  ylab("%Reduction of #Methods") 

barplot_perc_reduction_methods
```


There are some libs, such as DiUS_java-faker, for which the #Methods is equal zero

```{r echo=FALSE, warning=FALSE}
results %>% 
  select(Lib_gav, Nb_methods_original) %>% 
  filter(Nb_methods_original == 0) %>% 
  distinct(Lib_gav)
```



# Lib coverage

```{r echo=FALSE}
methods_coverage<- results %>%
  # filter(Lib_coverage > 0) %>% 
  select(Nb_methods_debloated, Lib_coverage) %>% 
  ggplot(aes(y = Nb_methods_debloated, x = Lib_coverage)) +
  geom_point()

classes_coverage <- results %>%
  # filter(Lib_coverage > 0) %>% 
  select(Nb_classes_debloated, Lib_coverage) %>% 
  ggplot(aes(y = Nb_classes_debloated, x = Lib_coverage)) +
  geom_point()

classes_coverage + methods_coverage + plot_layout(ncol = 1)
```



# Client plots

## Client Test results original vs test debloated

```{r echo=FALSE}
results$Client_original_test_error <- as.numeric(results$Client_original_test_error)

print("#Clients original with at least one test error: ")
results %>% filter(Client_original_test_error > 0) %>% nrow()
print("#Clients debloated with at least one test error: ")
results %>% filter(Client_debloat_test_error > 0) %>% nrow()

print("#Clients original with zero test error: ")
results %>% filter(Client_original_test_error == 0 ) %>% nrow()
print("#Clients debloated with zero test error: ")
results %>% filter(Client_debloat_test_error == 0) %>% nrow()

print("#Clients debloated with zero test error and at least one debloated test error: ")
results %>% filter(Client_original_test_error == 0 && Client_debloat_test_error != 0) %>% nrow()
print("#Clients debloated wigh zero test error and at least one debloated test error: ")
results %>% filter(Client_original_test_error != 0 && Client_debloat_test_error != 0) %>% nrow()

```

```{r echo=FALSE}
print("#Clients original with at least one test pass: ")
results %>% filter(Client_debloat_test_failing > 0) %>% nrow()
print("#Clients debloated with at least one test fail: ")
results %>% filter(Client_debloat_test_failing > 0) %>% nrow()

print("#Clients original with zero test fail: ")
results %>% filter(Client_debloat_test_failing == 0 ) %>% nrow()
print("#Clients debloated with zero test fail: ")
results %>% filter(Client_debloat_test_failing == 0) %>% nrow()

print("#Clients debloated with zero test fail and at least one debloated test fail: ")
results %>% filter(Client_debloat_test_failing == 0 && Client_debloat_test_failing != 0) %>% nrow()
print("#Clients debloated wigh zero test fail and at least one debloated test fail: ")
results %>% filter(Client_debloat_test_failing != 0 && Client_debloat_test_failing != 0) %>% nrow()
```


```{r echo=FALSE}
print("#Clients original with at least one test pass: ")
results %>% filter(Client_original_test_passing > 0) %>% nrow()
print("#Clients debloated with at least one test pass: ")
results %>% filter(Client_debloat_test_passing > 0) %>% nrow()

print("#Clients original with zero test pass: ")
results %>% filter(Client_original_test_passing == 0 ) %>% nrow()
print("#Clients debloated with zero test pass: ")
results %>% filter(Client_debloat_test_passing == 0) %>% nrow()

print("#Clients debloated with zero test pass and at least one debloated test pass: ")
results %>% filter(Client_original_test_passing == 0 && Client_debloat_test_passing != 0) %>% nrow()
print("#Clients debloated wigh zero test pass and at least one debloated test pass: ")
results %>% filter(Client_original_test_passing != 0 && Client_debloat_test_passing != 0) %>% nrow()

```

## Violin plots 

```{r echo=FALSE}
results_errors <- results %>% 
  filter(Client_debloat_test_error >= Client_original_test_error)

results_errors <- results_errors %>% 
  select(Client, Client_original_test_error, Client_debloat_test_error) %>% 
  gather(Client, test_errors, Client_original_test_error:Client_debloat_test_error)

# violin plot of the test errors
violinplot_errors <- results_errors %>%  
  # filter(test_errors != 0) %>%  # libs that have at least one test error
  ggplot(aes(x = Client, y = test_errors, fill = Client)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod"))  +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_errors.pdf", plot = violinplot_errors,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)

```

```{r echo=FALSE}
results_fails <- results %>% 
  select(Client, Client_debloat_test_failing, Client_original_test_failing) %>% 
  gather(Client, test_fails, Client_debloat_test_failing:Client_original_test_failing)

# violin plot of the test fails
violinplot_fails <- results_fails %>%  
  filter(test_fails != 0) %>%  # libs that have at least one test fail
  ggplot(aes(x = Client, y = test_fails, fill = Client)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod"))  +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_fails.pdf", plot = violinplot_fails,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
results_passs <- results %>% 
  select(Client, Client_original_test_passing, Client_debloat_test_passing) %>% 
  gather(Client, test_passs, Client_original_test_passing:Client_debloat_test_passing)

# violin plot of the test passs
violinplot_passs <- results_passs %>%  
  filter(test_passs != 0) %>%  # libs that have at least one test pass
  ggplot(aes(x = Client, y = test_passs, fill = Client)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_passs.pdf", plot = violinplot_passs,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```


```{r echo=FALSE}
violinplot_errors + violinplot_fails + violinplot_passs + plot_layout(ncol = 1)
```

## Bar plots

```{r echo=FALSE}
results_errors <- results %>% 
  select(Client, Client_original_test_error, Client_debloat_test_error) %>% 
  gather(Client, test_errors, Client_original_test_error:Client_debloat_test_error)

# barplot of the test errors
barplot_errors <- results_errors %>%  
  ggplot(aes(x = reorder(Client, test_errors), y = test_errors, fill = Client)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "clients") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod"))  +
  xlab(NULL)

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_errors.pdf", plot = barplot_errors, 
       height = 12, width = 10,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
results_fails <- results %>% 
  # filter(Client_debloat_test_failing != Client_debloat_test_failing) %>% 
  select(Client, Client_debloat_test_failing, Client_original_test_failing) %>% 
  gather(Client, test_fails, Client_debloat_test_failing:Client_original_test_failing)

# barplot of the test fails
barplot_fails <- results_fails %>%  
  ggplot(aes(x = reorder(Client, test_fails), y = test_fails, fill = Client)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "clients") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  xlab(NULL) +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_fails.pdf", plot = barplot_fails, 
       height = 12, width = 10,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
results_passs <- results %>% 
  # filter(Client_original_test_passing != Client_debloat_test_passing) %>% 
  select(Client, Client_original_test_passing, Client_debloat_test_passing) %>% 
  gather(Client, test_passs, Client_original_test_passing:Client_debloat_test_passing)

# barplot of the test passs
barplot_passs <- results_passs %>%  
  ggplot(aes(x = reorder(Client, test_passs), y = test_passs, fill = Client)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "clients") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  xlab(NULL) +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_passs.pdf", plot = barplot_passs, 
       height = 12, width = 10,  units = c("in"), device=cairo_pdf)
```


```{r echo=FALSE}
barplot_errors + barplot_fails + barplot_passs + plot_layout(ncol = 1)
```

