---
title: "Initial analysis"
author: César Soto Valero
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    css: main.css
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: false
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Import the header 
source("header.R")
# Clear the R environment
rm(list=ls())
```

# Prepare the Dataset

```{r echo=FALSE}
# Read the data
# raw_results <- read.delim("Data/raw_results_final_3.csv", sep = ",", header = T, stringsAsFactors = TRUE)
raw_results <- read.delim("Data/final_results_revision.csv", sep = ",", header = T, stringsAsFactors = TRUE)

# Prepare the data
results <- raw_results %>%
  filter(ID != "False") %>%  
  # Create Lib, Lib.gav, and Client variables
  mutate(Lib = paste(Lib.groupId, Lib.artifactId, sep = ":")) %>% 
  mutate(Lib.av = paste(Lib.artifactId, Lib.version, sep = ":")) %>% 
  mutate(Lib.gav = paste(Lib, Lib.version, sep = ":")) %>% 
  mutate(Client = paste(Client.groupId, Client.artifactId, sep = ":")) %>% 
  # Create
  mutate(Nb.test.debloat = (Lib.debloat.test.error + Lib.debloat.test.failing + Lib.debloat.test.passing)) %>% 
  filter(Nb.test.debloat == Lib.original.test.passing) %>% 
  select(-Nb.test.debloat) %>% 
  # Remove libs with weird executions due to config issues
  filter(ID != "FasterXML_woodstox_6.1.1" & 
           ID != "FasterXML_woodstox_6.0.2")
colnames(results)


# raw_results %>% filter(Nb.Dependenies == 1) %>% select(ID) %>% distinct()
# raw_results %>% filter(Nb.Dependenies > 1) %>% select(ID) %>% distinct()
```


```{r}
'%!in%' <- function(x,y)!('%in%'(x,y))
results <- results %>% filter(ID %!in% c("apache_sling-org-apache-sling-api_2.16.0", 
                             "jline_jline2_2.6", 
                             "liudongdong0909_mybatis-generator-core-fix_1.3.2",
                             "logstash_logstash-logback-encoder_4.8",
                             "logstash_logstash-logback-encoder_4.11",
                             "logstash_logstash-logback-encoder_5.3",
                             "vert-x3_vertx-unit_3.7.0",
                             "vert-x3_vertx-unit_3.6.3",
                             "vert-x3_vertx-unit_3.8.3"))

results <- results %>% distinct()
View(results)
```


## Coverage

```{r}
class_coverage <- results %>% 
  select(ID, Nb.class.original, Nb.debloated.classes) %>% 
  mutate(Lib.classes.coverage = (Nb.class.original - Nb.debloated.classes)*100/Nb.class.original) %>% 
  distinct()

summary(class_coverage$Lib.classes.coverage)
```




## Total unique Lib GAVs:

```{r echo=FALSE}
results %>% count(Lib.gav) %>% arrange(desc(n))
```

## Total unique Lib GAs:

```{r echo=FALSE}
results %>% count(Lib) %>% arrange(desc(n))
```

# Overall Lib debloat success

```{r echo=FALSE, warning=FALSE}
debloat_effectiveness_stacked_barplot <- results %>%
  select(Lib.gav, Debloat) %>% 
  distinct() %>% 
  count(Debloat) %>% 
  mutate(`Debloat result` = ifelse(Debloat == "True", "Success", "Failure")) %>% 
  ggplot(aes(x = "Libs", y = n, fill = `Debloat result`, label = n)) +
  geom_bar(stat = "identity", width = 0.75, position=position_dodge()) +
  geom_text(aes(label=n), size = 6, position=position_dodge(width=0.75), hjust=-0.25) +
  scale_y_continuous(limits = c(0, 270), breaks=c(0, 50, 100, 150, 200, 252), labels=c("0", "50", "100", "150","200","252")) +
  scale_fill_manual(values = c( "#ff1f5d", "#00cd6c")) +
  coord_flip() +
  ylab("\\# Libraries") +
  xlab(NULL) + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()
        ) 

results %>%
  select(Lib.gav, Debloat) %>% 
  distinct() %>% 
  filter(Debloat == "False")

# PLOT
debloat_effectiveness_stacked_barplot
save_figure(debloat_effectiveness_stacked_barplot, "Figures/debloat_effectiveness_stacked_barplot", 6, 2)
```

For the rest of the analysis, we exclude the libs for which the debloat fail. The current number of Libs, Versions, and Clients in the dataset are:

```{r echo=FALSE, warning=FALSE}

results <- results %>% 
  filter(Debloat == "True")

results %>% select(Lib) %>% distinct() %>% count()
results %>% select(Lib.gav) %>% distinct() %>% count()
results %>% select(Client) %>% distinct() %>% count()
```

# Distribution of versions per library

```{r echo=FALSE}
results %>% 
  select(Lib.artifactId, Lib.version) %>% 
  distinct() %>% 
  group_by(Lib.artifactId) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x= "Libs", y = n)) +
  geom_violin(fill="goldenrod") +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  xlab(NULL) +
  ylab("#Versions")+
  coord_flip()

results %>%
  select(Lib.artifactId, Lib.version) %>%
  distinct() %>%
  group_by(Lib.artifactId) %>%
  summarise(Nb.Versions = n()) %>%
  arrange(desc(Nb.Versions))
```

# Distribution of clients per library

```{r echo=FALSE}
results %>% 
  select(Lib.gav, Client) %>% 
  distinct() %>% 
  group_by(Lib.gav) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x= "Libs", y = n)) +
  geom_violin(fill="goldenrod") +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  xlab(NULL) +
  ylab("#Clients")+
  coord_flip()

results %>% 
    select(Lib.gav, Client) %>% 
  distinct() %>% 
  group_by(Lib.gav) %>% 
  summarise(Nb.Clients = n()) %>% 
  arrange(desc(Nb.Clients))
```

# Libs test results (global)

## Percentage of tests with errors

```{r}
results_debloat_errors <- results %>% 
  select(Lib, Lib.gav, Lib.debloat.test.error, Lib.debloat.test.failing, Lib.debloat.test.passing) %>% 
  distinct() %>% 
  group_by(Lib) %>% 
  summarise(errors = sum(Lib.debloat.test.error), failing = sum(Lib.debloat.test.failing), passing = sum(Lib.debloat.test.passing))

sum_errors <- sum(results_debloat_errors$errors)
sum_failing <- sum(results_debloat_errors$failing)
sum_passing <- sum(results_debloat_errors$passing)
perc_errors <- (sum_errors) * 100/sum_passing
perc_errors

```

## Number of tests with failures

```{r}
perc_failing <- (sum_failing) * 100/sum_passing
perc_failing
```

```{r}
debloat_nb_test_errors_failures_barplot <- 
  data.frame(`Test result` = c("Pass", "Error", "Failure"), n = c(353623, 38, 56)) %>% 
  rename(`Test result` = Test.result) %>% 
  ggplot(aes(x = "Libs", y = n, fill = `Test result`, label = n)) +
    geom_bar(stat = "identity", width = 0.75, position=position_dodge()) +
    geom_text(aes(label=n), size = 6, position=position_dodge(width=0.75), hjust=-0.1) +
    scale_fill_manual(values = c("#ff1f5d", "#ffc61e", "#00cd6c")) +
    coord_flip() +
    ylab("\\# Tests (log scale)") +
    xlab(NULL) + 
   scale_y_continuous(limits = c(0, 1500000), breaks=c(0, 1, 10, 100, 1000, 10000), trans="log1p") +
    # scale_y_log10(
    #   breaks = scales::trans_breaks("log10", function(x) 10 ^ x),
    #   labels = scales::trans_format("log10", scales::math_format(10 ^ .x))
    # ) +
    # scale_y_continuous(limits = c(0, 3500000), labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
          panel.grid.major.y = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank()) 
# PLOT
debloat_nb_test_errors_failures_barplot
save_figure(debloat_nb_test_errors_failures_barplot, "Figures/debloat_nb_test_errors_failures_stacked_barplot", 6, 2)
```

```{r}
df <- data.frame( `Test result`= c("Not all pass", "All pass"), n = c(26, 226))

debloat_nb_test_errors_failures_barplot <- 
  df %>% 
  rename(`Test result` = Test.result) %>% 
  ggplot(aes(x = "Libs", y = n, fill = factor(`Test result`, levels = rev(levels(`Test result`))) , label = n)) +
    geom_bar(stat = "identity", width = 0.75, position=position_dodge()) +
    geom_text(aes(label=n), size = 6, position=position_dodge(width=0.75), hjust=-0.1) +
    scale_fill_manual(values = c("#ff1f5d", "#00cd6c")) +
    coord_flip() +
    ylab("\\# Libraries") +
    xlab(NULL) + 
    labs(fill = "Tests result") +
    # scale_y_log10(
    #   breaks = scales::trans_breaks("log10", function(x) 10 ^ x),
    #   labels = scales::trans_format("log10", scales::math_format(10 ^ .x))
    # ) +
    scale_y_continuous(limits = c(0, 235)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
          panel.grid.major.y = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank()) 
# PLOT
debloat_nb_test_errors_failures_barplot
save_figure(debloat_nb_test_errors_failures_barplot, "Figures/debloat_nb_test_errors_failures_stacked_barplot", 6, 2)
```

## Libraries with Debloat Errors or Failures

```{r}
percentages <- results %>% 
  select(Lib.av, Lib.debloat.test.error, Lib.debloat.test.failing, Lib.debloat.test.passing) %>% 
  filter(Lib.debloat.test.error != 0 | Lib.debloat.test.failing != 0) %>% 
  mutate(Total = Lib.debloat.test.error + Lib.debloat.test.failing) %>% 
  mutate(Lib.debloat.test.error = round(Lib.debloat.test.error*100/Lib.debloat.test.passing, 2)) %>%
  mutate(Lib.debloat.test.failing = round(Lib.debloat.test.failing*100/Lib.debloat.test.passing, 2)) %>%
  mutate(Lib.debloat.test.error = ifelse(is.infinite(Lib.debloat.test.error), 100, Lib.debloat.test.error)) %>%
  mutate(Lib.debloat.test.failing = ifelse(is.na(Lib.debloat.test.failing), 0, Lib.debloat.test.failing)) %>%
  mutate(Total.percent = Lib.debloat.test.error + Lib.debloat.test.failing ) %>%
  distinct()

debloat_nb_test_errors_failures_lib_stacked_barplot <- results %>% 
  select(Lib.av, Lib.debloat.test.error, Lib.debloat.test.failing) %>% 
  filter(Lib.debloat.test.error != 0 | Lib.debloat.test.failing != 0) %>% 
  distinct() %>% 
  group_by(Lib.av) %>% 
  summarise(Error = sum(Lib.debloat.test.error), Failure = sum(Lib.debloat.test.failing)) %>% 
  gather(key = Error, value = Failure, - Lib.av) %>% 
  rename(`Test result` = Error, n = Failure) %>% 
  ggplot(aes(x = Lib.av, y = n, fill = `Test result`, label = n)) +
    geom_bar(stat = "identity", width = 0.9) +
    # geom_text(size = 4, position = position_stack(vjust = 0.5)) +
    scale_fill_manual(values = c( "#ff1f5d", "#ffc61e", "#00cd6c")) +
    coord_flip() +
    ylab("\\# Tests") +
    xlab(NULL) + 
    geom_text(aes(Lib.av, Total, label = paste(Total.percent, "\\%", sep=" "), fill = NULL, hjust = -0.1), data = percentages) +
    scale_y_continuous(limits = c(0, 40)) +
  
    theme(#axis.text.y=element_blank(),
          # axis.ticks.y=element_blank(),
          axis.text.y = element_text(size=10),
          panel.grid.major.y = element_blank())

debloat_nb_test_errors_failures_lib_stacked_barplot
save_figure(debloat_nb_test_errors_failures_lib_stacked_barplot, "Figures/debloat_nb_test_errors_failures_lib_stacked_barplot", 5.5, 3.5)
```

# Libraries and dependencies

## Library classes beanplot

```{r}
data <- results %>% 
  select(ID, Nb.class.original, Nb.debloated.classes) %>% 
  mutate(Nb.class.debloated = Nb.class.original - Nb.debloated.classes) %>% 
  select(ID, Nb.class.original, Nb.class.debloated) %>% 
  distinct() %>% 
  gather(Nb.class.original, Nb.class.debloated, -ID) %>% 
  rename(Lib = Nb.class.original, Classes = Nb.class.debloated)

tikz(file = "Figures/lib_classes_beanplot.tex", width = 4, height =3)

lib_classes_beanplot <- beanplot(
  Classes ~ Lib,
  data = data,
  side = "both",
  border = NA,
  col = list("#ffc61e", "#a6761d"),
  ll = 0,
  log = "auto",
  beanlines = "mean",
  horizontal = TRUE
)
legend("topleft", bty="n", c("\\#Classes original", "\\#Classes debloated"),
       fill = c("#a6761d", "#ffc61e"))

print(lib_classes_beanplot)
dev.off()
```

## Library methods beanplot

```{r}
data <- results %>% 
  select(ID, Nb.method.original, Nb.debloated.methods) %>% 
  mutate(Nb.method.debloated = Nb.method.original - Nb.debloated.methods) %>% 
  select(ID, Nb.method.original, Nb.method.debloated) %>% 
  distinct() %>% 
  gather(Nb.method.original, Nb.method.debloated, -ID) %>% 
  rename(Lib = Nb.method.original, Methods = Nb.method.debloated)

tikz(file = "Figures/lib_methods_beanplot.tex", width = 4, height =3)

lib_classes_beanplot <- beanplot(
  Methods ~ Lib,
  data = data,
  side = "both",
  border = NA,
  col = list("#ffc61e", "#a6761d"),
  ll = 0,
  log = "auto",
  horizontal = TRUE
)

legend("topright", bty="n", c("\\#Methods original", "\\#Methods debloated"),
       fill = c("#a6761d", "#ffc61e"))

print(lib_classes_beanplot)
dev.off()
```

## Dependency classes beanplot

```{r}
data <- results %>% 
  select(ID, Nb.dependeny.class, Nb.bloated.dependeny.class) %>% 
  mutate(Nb.dependeny.class.bloated = Nb.dependeny.class - Nb.bloated.dependeny.class) %>% 
  select(ID, Nb.dependeny.class, Nb.dependeny.class.bloated) %>% 
  distinct() %>% 
  gather(Nb.dependeny.class, Nb.dependeny.class.bloated, -ID) %>% 
  rename(Lib = Nb.dependeny.class, Classes = Nb.dependeny.class.bloated)

tikz(file = "Figures/deps_classes_beanplot.tex", width = 4, height =3)

lib_classes_beanplot <- beanplot(
  Classes ~ Lib,
  data = data,
  side = "both",
  border = NA,
  col = list("#ffc61e", "#a6761d"),
  ll = 0,
  bw="nrd0",
  log = "auto",
  horizontal = TRUE
)
legend("topright", bty="n", c("\\#Classes original", "\\#Classes debloated"),
       fill = c("#ffc61e", "#a6761d"))
```

## Dependency methods beanplot

```{r}
data <- results %>% 
  select(ID, Nb.dependeny.method, Nb.bloated.dependeny.method) %>% 
  mutate(Nb.dependeny.method.bloated = Nb.dependeny.method - Nb.bloated.dependeny.method) %>% 
  select(ID, Nb.dependeny.method.bloated, Nb.dependeny.method) %>% 
  distinct() %>% 
  gather(Nb.dependeny.method, Nb.dependeny.method.bloated, -ID) %>% 
  rename(Lib = Nb.dependeny.method, Methods = Nb.dependeny.method.bloated)

tikz(file = "Figures/deps_methods_beanplot.tex", width = 4, height = 3)

lib_classes_beanplot <- beanplot(
  Methods ~ Lib,
  data = data,
  side = "both",
  border = NA,
  col = list("#ffc61e", "#a6761d"),
  ll = 0,
  bw="nrd0",
  log = "auto",
  horizontal = TRUE
)
legend("topright", bty="n", c("\\#Methods original", "\\#Methods debloated"),
       fill = c("#ffc61e", "#a6761d"))

print(lib_classes_beanplot)
dev.off()
```

## Percentage of bloat in library classes and dependencies

```{r}
data <- results %>% 
  filter(Debloat == "True") %>% 
    filter(Lib.debloat.test.error == 0 & Lib.debloat.test.failing == 0) %>% 
  # Libraries with no dependencies
  mutate(Type = ifelse(Nb.dependeny.class == 0, "Library without dependency", "Library with dependencies")) %>% 
  select(ID, Type, Nb.class.original, Nb.debloated.classes, Nb.dependeny.class, Nb.bloated.dependeny.class) %>% 
  mutate(PercBloatClassesLib = (Nb.debloated.classes*100/Nb.class.original)) %>% 
  mutate(PercBloatClassesDeps = (Nb.bloated.dependeny.class*100/Nb.dependeny.class)) %>% 
  select(ID, PercBloatClassesLib, PercBloatClassesDeps) %>% 
  distinct() %>% 
  gather(PercBloatClassesLib, PercBloatClassesDeps, -ID) %>% 
  rename(Type = PercBloatClassesLib, Perc = PercBloatClassesDeps)

summary(data$Perc)

tikz(file = "Figures/bloat_libs_deps_bean.tex", width = 4.25, height = 2.75)

bloat_libs_deps_bean <- beanplot(
  Perc ~ Type,
  data = data,
  side = "both",
  method = "jitter",
  border = NA,
  col = list("#009ade", "#b5e3eb"),
  ll = 0.05,
  bw="nrd0",
  log = "auto",
  horizontal = TRUE,
  yaxt='n',
  # ylim = c(0,100),
  # ylab = "Libraries",
  xlab = "\\% Classes"
)
axis(2, at=1:1, labels=c("Libraries"))
legend("topright", bty="n", c("\\% Bloat in libraries", "\\% Bloat in dependencies"),
       fill = c("#009ade", "#b5e3eb"))

print(bloat_libs_deps_bean)
dev.off()
  
```

## Library classes area

```{r}
data <- results %>% 
  filter(Debloat == "True") %>% 
  filter(Lib.debloat.test.error == 0 & Lib.debloat.test.failing == 0) %>% 
  # Libraries with no dependencies
  filter(Nb.dependeny.class == 0) %>% 
  select(ID, Nb.class.original, Nb.debloated.classes) %>% 
  mutate(Bloated = (Nb.debloated.classes*100/Nb.class.original)) %>% 
  mutate(Used = 100 - Bloated) %>% 
  select(ID, Used, Bloated) %>%
  distinct() %>%
  gather(Used, Bloated, -ID) %>%
  rename(`Usage status` = Used, Perc = Bloated) %>% 
  arrange(desc(Perc)) 
 
data$ID <- as.factor(data$ID)
data <- data %>% mutate(ID = fct_reorder(ID, Perc))
data$NumID <- as.numeric(data$ID)

data_used <- data %>% filter(`Usage status` == "Used")
data_used$NumID <- c(1:(nrow(data)/2))
data_bloated <- data %>% filter(`Usage status` == "Bloated")
data_bloated$NumID <- c((nrow(data)/2):1)

data <- bind_rows(data_bloated, data_used)
data$`Usage status` <- factor(data$`Usage status`, levels = c("Used", "Bloated"))

lib_classes_area <- data %>% 
  ggplot(aes(x = NumID, y = Perc, fill = `Usage status`)) +
  geom_area(aes(fill = `Usage status`), position = "fill") +
  xlab(NULL) +
  ylab("\\% Classes") +
  # scale_y_continuous(labels = scales::percent) +
  theme( legend.title = element_blank()) +
  scale_y_continuous(labels = function(x) paste0(x*100, "\\%")) +
  scale_x_continuous(limits = c(0, 141), 
                     breaks=c(1, 25 , 50, 75, 100, 122, (nrow(data)/2)),
                     labels=c("1", "25", "50", "75", "100", "125", "141")) +
  scale_fill_manual(values = c("#03E888", "#FF2E3A")) +
  theme(
        # panel.grid.major.y = element_blank()
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()
        )
lib_classes_area
save_figure(lib_classes_area, "Figures/lib_classes_area", 6, 2)

#03E888
#FF2E3A
```

## Library methods barplot

```{r}
data2 <- results %>% 
  filter(Debloat == "True") %>% 
  filter(Lib.debloat.test.error == 0 & Lib.debloat.test.failing == 0) %>% 
  # Libraries with no dependencies
  filter(Nb.dependeny.class == 0) %>% 
  select(ID, Nb.method.original, Nb.debloated.methods) %>% 
  mutate(Bloated = (Nb.debloated.methods*100/Nb.method.original)) %>% 
  mutate(Used = 100 - Bloated) %>% 
  select(ID, Used, Bloated) %>%
  distinct() %>%
  mutate(Used = ifelse(is.na(Used), 100, Used), Bloated = ifelse(is.na(Bloated), 0, Bloated)) %>% 
  gather(Used, Bloated, -ID) %>%
  rename(Type.methods = Used, Perc.methods = Bloated) %>% 
  arrange(desc(Perc.methods)) %>% 
  mutate(Perc.methods = ifelse(is.na(Perc.methods), 0, Perc.methods))

# data <- data %>% filter(`Usage status` == "Used")
data$ID <- as.character(data$ID)
data2$ID <- as.character(data2$ID)
data3 <- inner_join(data, data2, by = "ID")

lib_methods_bar <- data3 %>% 
  filter(Type.methods == "Bloated" & `Usage status` == "Used") %>% 
  select(NumID, Perc.methods) %>% 
  ggplot(aes(x = NumID, y = Perc.methods)) +
  geom_bar(stat = "identity", fill = "#a6761d", width = 2) +
  scale_x_continuous(limits = c(0, 128), 
                     breaks=c(0, 50, 100, 128),
                     labels=c("1", "50", "100", "129")) +
  scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "\\%")) +
  xlab(NULL) +
  ylab("\\% Methods") +
  theme(
        # panel.grid.major.y = element_blank()
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()
        )

lib_methods_bar
save_figure(lib_methods_bar, "Figures/lib_methods_bar", 6, 1.75)


# Area chart

lib_methods_area <- data3 %>% 
  filter(`Usage status` == "Used") %>% 
  ggplot(aes(x = NumID, y = Perc.methods, fill = Type.methods)) +
  geom_area(aes(fill = Type.methods), position = "fill") +
  ylab("\\% Methods") +
  xlab(NULL) +
  # scale_y_continuous(labels = scales::percent) +
  theme( legend.title = element_blank()) +
  scale_x_continuous(limits = c(1, 119), 
                     breaks=c(1, 25, 50, 75, 100, 119),
                     labels=c("1", "25", "50", "75", "100", "119")) +
  scale_y_continuous(labels = function(x) paste0(x*100, "\\%")) +
  # scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "\\%")) +
  scale_fill_manual(values = c("#a6761d", "#ffc61e")) +
  theme(
        # panel.grid.major.y = element_blank()
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()
        ) +
  theme(legend.position = "none")

lib_methods_area
save_figure(lib_methods_area, "Figures/lib_methods_area", 6, 1.5)

```

## Dependency classes area

```{r}
data <- results %>% 
  filter(Debloat == "True") %>% 
  filter(Lib.debloat.test.error == 0 & Lib.debloat.test.failing == 0) %>% 
  select(ID, Nb.class.original, Nb.dependeny.class, Nb.bloated.dependeny.class, Nb.debloated.classes) %>% 
  filter(Nb.dependeny.class > 0) %>% 
  mutate(Bloated = ((Nb.bloated.dependeny.class +Nb.debloated.classes)*100/(Nb.dependeny.class +Nb.class.original))) %>% 
  mutate(Used = 100 - Bloated) %>% 
  select(ID, Used, Bloated) %>%
  distinct() %>%
  gather(Used, Bloated, -ID) %>%
  rename(`Usage status` = Used, Perc = Bloated) %>% 
  arrange(desc(Perc)) 
 
data$NumID <- as.factor(data$ID)
data <- data %>% mutate(ID = fct_reorder(ID, Perc))
data$NumID <- as.numeric(data$ID)

data_used <- data %>% filter(`Usage status` == "Used")
data_used$NumID <- c(1:(nrow(data)/2))
data_bloated <- data %>% filter(`Usage status` == "Bloated")
data_bloated$NumID <- c((nrow(data)/2):1)

data <- bind_rows(data_used, data_bloated)

deps_classes_area <- data %>% 
  ggplot(aes(x = NumID, y = Perc, fill = `Usage status`)) +
  geom_area(aes(fill = `Usage status`), position = "fill") +
  xlab(NULL) +
  ylab(NULL) +
  scale_y_continuous(labels = function(x) paste0(x*100, "\\%")) +
  # theme( legend.title = element_blank()) +
  scale_x_continuous(limits = c(0, (nrow(data)/2)), breaks=c(1,25, 50,75, 100, (nrow(data)/2)), labels=c("1", "25", "50","75" ,"100", "107")) +
  scale_fill_manual(values = c("#a6761d", "#ffc61e")) +
  theme(
        # panel.grid.major.y = element_blank()
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()
        )
  
deps_classes_area
save_figure(deps_classes_area, "Figures/deps_classes_area", 6, 2)
```

## Dependency methods barplot

```{r}
data2 <- results %>% 
  filter(Debloat == "True") %>% 
  filter(Lib.debloat.test.error == 0 & Lib.debloat.test.failing == 0) %>% 
  # Libraries with no dependencies
  filter(Nb.dependeny.class > 0) %>% 
  select(ID, Nb.method.original, Nb.debloated.methods) %>% 
  mutate(Bloated = (Nb.debloated.methods*100/Nb.method.original)) %>% 
  mutate(Used = 100 - Bloated) %>% 
  select(ID, Used, Bloated) %>%
  distinct() %>%
  gather(Used, Bloated, -ID) %>%
  rename(Type.methods = Used, Perc.methods = Bloated) %>% 
  arrange(desc(Perc.methods)) %>% 
  mutate(Perc.method = ifelse(is.na(Perc.methods), 50,Perc.methods ))


# data <- data %>% filter(`Usage status` == "Used")
data$ID <- as.character(data$ID)
data2$ID <- as.character(data2$ID)
data3 <- inner_join(data, data2, by = "ID")

lib_methods_bar <- data3 %>% 
  filter(Type.methods == "Bloated" & `Usage status` == "Used") %>% 
  select(NumID, Perc.methods) %>% 
  ggplot(aes(x = NumID, y = Perc.methods)) +
  geom_bar(stat = "identity", fill = "#a6761d", width = 2) +
  scale_x_continuous(limits = c(0, (nrow(data3)/4)), 
                     breaks=c(0, 25, 50, 75, 100, (nrow(data3)/4)),
                     labels=c("1", "25", "50","75", "100", "107")) +
  scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "\\%")) +
  xlab(NULL) +
  ylab(NULL) +
  theme(
        # panel.grid.major.y = element_blank()
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()
        )

lib_methods_bar
save_figure(lib_methods_bar, "Figures/deps_methods_bar", 6, 1.75)


# Area chart
deps_methods_area <- data3 %>% 
   filter(`Usage status` == "Bloated") %>% 
  ggplot(aes(x = NumID, y = Perc.methods, fill = Type.methods)) +
  geom_area(aes(fill = Type.methods), position = "fill") +
  ylab(NULL) +
  xlab(NULL) +
  # scale_y_continuous(labels = scales::percent) +
  theme( legend.title = element_blank()) +
  scale_x_continuous(limits = c(0, 107), breaks=c(1, 25, 50, 75, 100, 107), labels=c("1","25", "50","75", "100", "107")) +
  scale_y_continuous(labels = function(x) paste0(x*100, "\\%")) +
  scale_fill_manual(values = c("#a6761d", "#ffc61e")) +
  theme(
        # panel.grid.major.y = element_blank()
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()
        ) +
  theme(legend.position = "none")
  
deps_methods_area
save_figure(deps_methods_area, "Figures/deps_methods_area", 6, 1.5)

```

```{r}
results %>% 
  filter(ID == "jettison-json_jettison_1.3.2") %>% 
  # filter(Nb.debloated.classes == 0) %>% 
  select(Nb.method.original, Nb.debloated.methods, Nb.dependeny.method, Nb.bloated.dependeny.method)

```

## Dependency methods area

```{r}
data <- results %>% 
  select(ID, Nb.dependeny.method, Nb.bloated.dependeny.method) %>% 
  filter(Nb.dependeny.method > 0) %>% 
  mutate(Bloated = (Nb.bloated.dependeny.method*100/Nb.dependeny.method)) %>% 
  mutate(Used = 100 - Bloated) %>% 
  select(ID, Used, Bloated) %>%
  distinct() %>%
  gather(Used, Bloated, -ID) %>%
  rename(Type = Used, Perc = Bloated) %>% 
  arrange(desc(Perc)) 
 
data$ID <- as.factor(data$ID)
data <- data %>% mutate(ID = fct_reorder(ID, Perc))
data$ID <- as.numeric(data$ID)

data_used <- data %>% filter(Type == "Used")
data_used$ID <- c(1:(nrow(data)/2))
data_bloated <- data %>% filter(Type == "Bloated")
data_bloated$ID <- c(1:(nrow(data)/2))

data <- bind_rows(data_used, data_bloated)

deps_methods_area <- data %>% 
  ggplot(aes(x = ID, y = Perc, fill = Type)) +
  geom_area(aes(fill = Type), position = "fill") +
  xlab(NULL) +
  ylab("\\% Methods") +
  # scale_y_continuous(labels = scales::percent) +
  theme( legend.title = element_blank()) +
  scale_x_continuous(limits = c(0, (nrow(data)/2)), breaks=c(1, (nrow(data)/2)), labels=c("1", "124")) +
  scale_fill_manual(values = c("#a6761d", "#ffc61e")) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())
  
deps_methods_area
save_figure(deps_methods_area, "Figures/deps_methods_area", 5, 2.5)
```

# Completely removed dependencies

```{r echo=FALSE}
data <- results %>% 
  filter(Debloat == "True") %>%
  select(ID, Nb.Dependenies, Nb.bloated.dependenies) %>% 
  distinct()

a <- sum(data$Nb.Dependenies)
b <- sum(data$Nb.bloated.dependenies)

b <- round(b*100/a, 2)
a <- 100 - b

df <- data.frame(`Dependency status` = c("Used", "Bloated"), n = c(a, b))
  
deps_status_total <- df %>% ggplot(aes(x = "Deps", y = n, fill = Dependency.status, label = n)) +
  geom_bar(stat = "identity", width = 0.75) +
  geom_text(aes(label=n), size = 6, position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = c( "#a6761d", "#ffc61e")) +
  coord_flip() +
  ylab("\\% Dependencies") +
  xlab(NULL) + 
  scale_y_continuous(labels = function(x) paste0(x, "\\%")) +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()
        ) 

deps_status_total
save_figure(deps_status_total, "Figures/deps_status_total", 6, 2.1)

```

# Debloat summary

```{r}
data <- results %>% 
  filter(Debloat == "True") %>% 
  filter(Lib.debloat.test.error == 0 & Lib.debloat.test.failing == 0) %>% 
  select(ID, Nb.class.original, Nb.method.original, Nb.debloated.classes, Nb.debloated.methods) %>% 
  distinct()

sum(data$Nb.debloated.classes)*100/sum(data$Nb.class.original)
sum(data$Nb.debloated.methods)*100/sum(data$Nb.method.original)


```

# Lib coverage

```{r echo=FALSE}
data <- results %>%
  filter(Debloat == "True") %>% 
  # filter(Nb.dependeny.class > 0) %>% 
  select(ID, Nb.class.original, Nb.debloated.classes, Lib.coverage, Lib.dep.coverage, Lib.all.coverage, Nb.method.original, Nb.debloated.methods) %>% 
  mutate(Perc.bloated.methods = Nb.debloated.methods*100/Nb.method.original) %>% 
  select(ID, Perc.bloated.methods, Lib.coverage, Lib.dep.coverage, Lib.all.coverage) %>% 
  distinct() %>% 
  ggplot(aes(Perc.bloated.methods, Lib.coverage)) +
  geom_point() +
  geom_smooth(method = "lm")

a <- data %>% select(ID, Perc.bloated.classes, Lib.coverage) %>% mutate(Type = "Lib.coverage") %>% rename(Coverage =
                                                                                                           Lib.coverage)

b <- data %>% select(ID, Perc.bloated.classes, Lib.dep.coverage) %>% mutate(Type = "Lib.dep.coverage") %>% rename(Coverage = Lib.dep.coverage)

c <- data %>% select(ID, Perc.bloated.classes, Lib.coverage) %>% mutate(Type = "LibCoverage") %>% rename(Coverage =
                                                                                                           Lib.coverage)




%>% 
  gather(ID, Perc.bloated.classes, -c(ID,Lib.coverage)) %>% 

  
  

classes_coverage + methods_coverage + plot_layout(ncol = 1)
```

# Size of the JAR

```{r echo=FALSE}
library(tibble)
results_size <- results %>%
  filter(Debloat == "True") %>% 
  select(ID, Size.original.jar, Size.debloat.jar) %>% 
  mutate(Perc.reduction.size = ((Size.original.jar - Size.debloat.jar)*100/Size.original.jar)) %>% 
  distinct() %>% 
  arrange(desc(Perc.reduction.size)) %>% 
  mutate(Perc.reduction.size = ifelse(Perc.reduction.size < 0, 0, Perc.reduction.size)) %>% 
  filter(Perc.reduction.size != 0)

# violin plot of the sizes
lib_size_violinplot <- results_size %>%  
  ggplot(aes(x = "JARs", y =Perc.reduction.size)) +
  geom_violin(fill = "#a0b1ba") +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100), trans="log1p") +
  # scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  coord_flip() +
  ylab("\\% Reduction (log scale)") +
  xlab("JARs") +
  theme(legend.position = "none",
        axis.text.y=element_blank(),)

lib_size_violinplot

save_figure(lib_size_violinplot, "Figures/lib_size_violinplot", 6, 2)

```

<!-- ```{r echo=FALSE} -->

<!-- boxplot_libs_classes_used <- results %>% -->

<!--   select(Lib_gav, nbLibUsedClasses) %>%  -->

<!--   distinct() %>% -->

<!--   ggplot(aes(x = "Libs", y = nbLibUsedClasses)) + -->

<!--   geom_violin(fill="dodgerblue3") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Classes used") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- boxplot_libs_classes_bloated <- results %>%  -->

<!--   select(Lib_gav, nbLibBloatedClasses) %>%  -->

<!--   distinct() %>% -->

<!--   ggplot(aes(x = "Libs", y = nbLibBloatedClasses)) + -->

<!--   geom_violin(fill="dodgerblue3") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Classes bloated") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- boxplot_libs_methods_used <- results %>%  -->

<!--   select(Lib_gav, nbLibUsedMethods) %>%  -->

<!--   distinct() %>%  -->

<!--   ggplot(aes(x = "Libs", y = nbLibUsedMethods)) + -->

<!--   geom_violin(fill="goldenrod") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Methods used") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- boxplot_libs_methods_bloated <- results %>%  -->

<!--   select(Lib_gav, nbLibBloatedMethods) %>%  -->

<!--   distinct() %>%  -->

<!--   ggplot(aes(x = "Libs", y = nbLibBloatedMethods)) + -->

<!--   geom_violin(fill="goldenrod") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Methods bloated") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- debloat_classes_methods_libs <- boxplot_libs_classes_used + boxplot_libs_methods_used + boxplot_libs_classes_bloated + boxplot_libs_methods_bloated -->

<!-- debloat_classes_methods_libs -->

<!-- ggsave(filename = "Figures/analysis_initial/debloat_classes_methods_libs.pdf", plot = debloat_classes_methods_libs,  -->

<!--        height = 4, width = 7,  units = c("in"), device=cairo_pdf) -->

<!-- ``` -->

<!-- ## Dependencies -->

<!-- ```{r echo=FALSE} -->

<!-- boxplot_deps_classes_used <- results %>%  -->

<!--   select(Lib_gav, nbDepsUsedClasses) %>%  -->

<!--   distinct() %>%  -->

<!--   ggplot(aes(x = "Deps", y = nbDepsUsedClasses)) + -->

<!--   geom_violin(fill="dodgerblue3") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Classes used") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- boxplot_deps_classes_bloated <- results %>%  -->

<!--   select(Lib_gav, nbDepsBloatedClasses) %>%  -->

<!--   distinct() %>%  -->

<!--   ggplot(aes(x = "Deps", y = nbDepsBloatedClasses)) + -->

<!--   geom_violin(fill="dodgerblue3") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Classes bloated") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- boxplot_deps_methods_used <- results %>%  -->

<!--   select(Lib_gav, nbDepsUsedMethods) %>%  -->

<!--   distinct() %>%  -->

<!--   ggplot(aes(x = "Deps", y = nbDepsUsedMethods)) + -->

<!--   geom_violin(fill="goldenrod") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Methods used") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- boxplot_deps_methods_bloated <- results %>%  -->

<!--   select(Lib_gav, nbDepsBloatedMethods) %>%  -->

<!--   distinct() %>%  -->

<!--   ggplot(aes(x = "Deps", y = nbDepsBloatedMethods)) + -->

<!--    geom_violin(fill="goldenrod") + -->

<!--   geom_boxplot(width = 0.05) + -->

<!--   ylab("#Methods bloated") + -->

<!--   xlab(NULL) + -->

<!--   scale_y_continuous( -->

<!--     breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), -->

<!--     trans = "log1p" -->

<!--   ) + -->

<!--   coord_flip() -->

<!-- debloat_classes_methods_deps <- boxplot_deps_classes_used + boxplot_deps_methods_used + boxplot_deps_classes_bloated + boxplot_deps_methods_bloated  -->

<!-- debloat_classes_methods_deps -->

<!-- ggsave(filename = "Figures/analysis_initial/debloat_classes_methods_deps.pdf", plot = debloat_classes_methods_deps,  -->

<!--        height = 4, width = 7,  units = c("in"), device=cairo_pdf) -->

<!-- ``` -->

# Libs Classes

```{r echo=FALSE}
results_classes <- results %>% 
  mutate(Nb_classes_debloated = Nb_classes_original - Nb_debloated_classes) %>% 
  select(Lib_gav, Nb_classes_original, Nb_classes_debloated) %>% 
  distinct() %>% 
  gather(Libs, Classes, Nb_classes_original:Nb_classes_debloated) %>% 
  distinct()

# violin plot of the classes
violinplot_classes <- results_classes %>%  ggplot(aes(x = Libs, y = Classes, fill = Libs)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values = c("goldenrod","dodgerblue3")) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x="Libs", y="#Classes")

violinplot_classes

a <- results_classes %>% filter(Libs == "Nb_classes_original")
summary(a)
b <- results_classes %>% filter(Libs == "Nb_classes_debloated")
summary(b)

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_classes.pdf", plot = violinplot_classes,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}

# barplot of the classes
barplot_classes <- results_classes %>%  
  ggplot(aes(x = reorder(Lib_gav, Classes), y = Classes, fill = Libs)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(y = "#Classes", x="Libs") +
  coord_flip() +
  scale_fill_manual(values = c("goldenrod","dodgerblue3")) +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6)) +
     theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

barplot_classes

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_classes.pdf", plot = barplot_classes , 
       height = 10, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
perc_reduction_classes <- results %>% 
   mutate(Nb_classes_debloated = Nb_classes_original - Nb_debloated_classes) %>% 
  select(Lib_gav, Nb_classes_original, Nb_classes_debloated) %>% 
  mutate(Perc_reduction = ((Nb_classes_original - Nb_classes_debloated)/Nb_classes_original)*100) %>% 
  select(Lib_gav, Perc_reduction) %>% 
  distinct()

# barplot of the methods
barplot_perc_reduction_classes <- perc_reduction_classes %>% 
  ggplot(aes(x = reorder(Lib_gav, Perc_reduction), y = Perc_reduction)) +
  geom_bar(stat = "identity", position = position_dodge(), fill = "dodgerblue3") +
  labs(x = "libs") +
  coord_flip() +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6)) +
  ylab("%Reduction of #Classes") +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

barplot_perc_reduction_classes
```

# Libs methods

```{r echo=FALSE}
results_methods <- results %>% 
  mutate(Nb_methods_debloated = Nb_methods_original - Nb_debloated_methods) %>% 
  select(Lib_gav, Nb_methods_original, Nb_methods_debloated) %>% 
  gather(libs, methods, Nb_methods_original:Nb_methods_debloated) %>% 
  distinct()

# violin plot of the methods
violinplot_methods <- results_methods %>% 
  ggplot(aes(x = libs, y = methods, fill = libs)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x="Libs", y="#Classes")

violinplot_methods

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_methods.pdf", plot = violinplot_methods,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
# barplot of the methods
barplot_methods <- results_methods %>%  ggplot(aes(x = reorder(Lib_gav, methods), y = methods, fill = libs)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "libs") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6)) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

barplot_methods

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_methods.pdf", plot = barplot_methods, 
       height = 10, width = 7,  units = c("in"), device=cairo_pdf)
```

Percentage of methods reduced per library.

```{r echo=FALSE}
perc_reduction_methods <- results %>% 
    mutate(Nb_methods_debloated = Nb_methods_original - Nb_debloated_methods) %>% 
  select(Lib_gav, Nb_methods_original, Nb_methods_debloated) %>% 
  mutate(Perc_reduction = ((Nb_methods_original - Nb_methods_debloated)/Nb_methods_original)*100) %>% 
  select(Lib_gav, Perc_reduction) %>% 
  distinct()

# barplot of the methods
barplot_perc_reduction_methods <- perc_reduction_methods %>% 
  ggplot(aes(x = reorder(Lib_gav, Perc_reduction), y = Perc_reduction)) +
  geom_bar(stat = "identity", position = position_dodge(), fill = "dodgerblue3") +
  labs(x = "libs") +
  coord_flip() +
  theme(axis.text.x = element_text(hjust = 1, size =  6), 
        axis.text.y = element_text(hjust = 1, size =  6)) +
  ylab("%Reduction of #Methods")  +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

barplot_perc_reduction_methods
```

There are some libs, such as DiUS_java-faker, for which the \#Methods is equal zero. These are those libraries:

```{r echo=FALSE, warning=FALSE}
results %>% 
  select(Lib_gav, Nb_methods_original) %>% 
  filter(Nb_methods_original == 0) %>% 
  distinct(Lib_gav)
```

# Client plots

## Client Test results original vs test debloated

```{r echo=FALSE}
results$Client_original_test_error <- as.numeric(results$Client_original_test_error)

print("#Clients original with at least one test error: ")
results %>% filter(Client_original_test_error > 0) %>% nrow()
print("#Clients debloated with at least one test error: ")
results %>% filter(Client_debloat_test_error > 0) %>% nrow()

print("#Clients original with zero test error: ")
results %>% filter(Client_original_test_error == 0 ) %>% nrow()
print("#Clients debloated with zero test error: ")
results %>% filter(Client_debloat_test_error == 0) %>% nrow()

print("#Clients debloated with zero test error and at least one debloated test error: ")
results %>% filter(Client_original_test_error == 0 && Client_debloat_test_error != 0) %>% nrow()
print("#Clients debloated wigh zero test error and at least one debloated test error: ")
results %>% filter(Client_original_test_error != 0 && Client_debloat_test_error != 0) %>% nrow()

```

```{r echo=FALSE}
print("#Clients original with at least one test pass: ")
results %>% filter(Client_debloat_test_failing > 0) %>% nrow()
print("#Clients debloated with at least one test fail: ")
results %>% filter(Client_debloat_test_failing > 0) %>% nrow()

print("#Clients original with zero test fail: ")
results %>% filter(Client_debloat_test_failing == 0 ) %>% nrow()
print("#Clients debloated with zero test fail: ")
results %>% filter(Client_debloat_test_failing == 0) %>% nrow()

print("#Clients debloated with zero test fail and at least one debloated test fail: ")
results %>% filter(Client_debloat_test_failing == 0 && Client_debloat_test_failing != 0) %>% nrow()
print("#Clients debloated wigh zero test fail and at least one debloated test fail: ")
results %>% filter(Client_debloat_test_failing != 0 && Client_debloat_test_failing != 0) %>% nrow()
```

```{r echo=FALSE}
print("#Clients original with at least one test pass: ")
results %>% filter(Client_original_test_passing > 0) %>% nrow()
print("#Clients debloated with at least one test pass: ")
results %>% filter(Client_debloat_test_passing > 0) %>% nrow()

print("#Clients original with zero test pass: ")
results %>% filter(Client_original_test_passing == 0 ) %>% nrow()
print("#Clients debloated with zero test pass: ")
results %>% filter(Client_debloat_test_passing == 0) %>% nrow()

print("#Clients debloated with zero test pass and at least one debloated test pass: ")
results %>% filter(Client_original_test_passing == 0 && Client_debloat_test_passing != 0) %>% nrow()
print("#Clients debloated wigh zero test pass and at least one debloated test pass: ")
results %>% filter(Client_original_test_passing != 0 && Client_debloat_test_passing != 0) %>% nrow()

```

## Violin plots

```{r echo=FALSE}
results_errors <- results %>% 
  filter(Client_debloat_test_error >= Client_original_test_error)

results_errors <- results_errors %>% 
  select(Client, Client_original_test_error, Client_debloat_test_error) %>% 
  gather(Client, test_errors, Client_original_test_error:Client_debloat_test_error)

# violin plot of the test errors
violinplot_errors <- results_errors %>%  
  # filter(test_errors != 0) %>%  # libs that have at least one test error
  ggplot(aes(x = Client, y = test_errors, fill = Client)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod"))  +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_errors.pdf", plot = violinplot_errors,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)

```

```{r echo=FALSE}
results_fails <- results %>% 
  select(Client, Client_debloat_test_failing, Client_original_test_failing) %>% 
  gather(Client, test_fails, Client_debloat_test_failing:Client_original_test_failing)

# violin plot of the test fails
violinplot_fails <- results_fails %>%  
  filter(test_fails != 0) %>%  # libs that have at least one test fail
  ggplot(aes(x = Client, y = test_fails, fill = Client)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod"))  +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_fails.pdf", plot = violinplot_fails,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
results_passs <- results %>% 
  select(Client, Client_original_test_passing, Client_debloat_test_passing) %>% 
  gather(Client, test_passs, Client_original_test_passing:Client_debloat_test_passing)

# violin plot of the test passs
violinplot_passs <- results_passs %>%  
  filter(test_passs != 0) %>%  # libs that have at least one test pass
  ggplot(aes(x = Client, y = test_passs, fill = Client)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_y_continuous(breaks=c(0, 1,10,100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000), trans="log1p") +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  xlab(NULL) +
  coord_flip() +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/violinplot_passs.pdf", plot = violinplot_passs,
       height = 5, width = 7,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
violinplot_errors + violinplot_fails + violinplot_passs + plot_layout(ncol = 1)
```

## Bar plots

```{r echo=FALSE}
results_errors <- results %>% 
  select(Client, Client_original_test_error, Client_debloat_test_error) %>% 
  gather(Client, test_errors, Client_original_test_error:Client_debloat_test_error)

# barplot of the test errors
barplot_errors <- results_errors %>%  
  ggplot(aes(x = reorder(Client, test_errors), y = test_errors, fill = Client)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "clients") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod"))  +
  xlab(NULL)

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_errors.pdf", plot = barplot_errors, 
       height = 12, width = 10,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
results_fails <- results %>% 
  # filter(Client_debloat_test_failing != Client_debloat_test_failing) %>% 
  select(Client, Client_debloat_test_failing, Client_original_test_failing) %>% 
  gather(Client, test_fails, Client_debloat_test_failing:Client_original_test_failing)

# barplot of the test fails
barplot_fails <- results_fails %>%  
  ggplot(aes(x = reorder(Client, test_fails), y = test_fails, fill = Client)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "clients") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  xlab(NULL) +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_fails.pdf", plot = barplot_fails, 
       height = 12, width = 10,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
results_passs <- results %>% 
  # filter(Client_original_test_passing != Client_debloat_test_passing) %>% 
  select(Client, Client_original_test_passing, Client_debloat_test_passing) %>% 
  gather(Client, test_passs, Client_original_test_passing:Client_debloat_test_passing)

# barplot of the test passs
barplot_passs <- results_passs %>%  
  ggplot(aes(x = reorder(Client, test_passs), y = test_passs, fill = Client)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_y_continuous(
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000),
    trans = "log1p"
  ) +
  labs(x = "clients") +
  coord_flip() +
  scale_fill_manual(values = c("dodgerblue3","goldenrod")) +
  xlab(NULL) +
  theme(legend.position = "none")

# save the plot
ggsave(filename = "Figures/analysis_initial/barplot_passs.pdf", plot = barplot_passs, 
       height = 12, width = 10,  units = c("in"), device=cairo_pdf)
```

```{r echo=FALSE}
barplot_errors + barplot_fails + barplot_passs + plot_layout(ncol = 1)
```
